|

### 2020-11-29 manuscript/article.Rmd
commit 4 11/28

```{r, message=FALSE, warning=FALSE, echo=FALSE}
## Starting

# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)

set.seed(732578) # From random.org

@@

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[4])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[3])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[1])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[2])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

@@

@@

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Clean up
rm(list = ls())

## Starting
set.seed(732578) # From random.org

@@

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

@@

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.2cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.5cm}}
\caption{Papers included in the meta-analysis, listed alphabetically by last name}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & OLS & M\\
R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & OLS & M\\
T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & IV & NM\\
\begin{tabular}[t]{@{}l@{}}T. Bjedov,\\ S. Lapointe \& \\T. Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}J. Drew \& \\ B. Dollery\end{tabular} & The Price of Democracy? Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & IV & NM\\
\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}B. Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & IV & M\\
\begin{tabular}[t]{@{}l@{}}B. Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}P. Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government? Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}C. Schaltegger \& \\ L. Feld\end{tabular} & Do Large Cabinets Favor Large Governments? Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}E. Stein,\\ E. Talvi \& \\ A. Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub. & 1998 & Multiple (26) & OLS & NM\\ [1ex]
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation). Country codes follow the ISO 3166-1 alpha-3 international standard.}
\end{minipage}
\end{longtable}

\normalsize

@@

```latex
\vspace{.5cm}

\begin{table}[htpb]
\caption{Meta Regression Results}
\label{tab:regressions}
\footnotesize
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}
```
